% !TeX program = pdflatex
% !TeX root = FeynHelpersHowToCite.tex

\documentclass[../FeynHelpersManual.tex]{subfiles}
\begin{document}
\hypertarget{feynhelpershowtocite}{
\section{FeynHelpersHowToCite}\label{feynhelpershowtocite}\index{FeynHelpersHowToCite}}

\texttt{FeynHelpersHowToCite[\allowbreak{}]} lists publications that
should be cited when mentioning FeynHelpers in scientific works.

\subsection{See also}

\hyperlink{toc}{Overview}

\subsection{Examples}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{FeynHelpersHowToCite}\OperatorTok{[]}
\end{Highlighting}
\end{Shaded}

\begin{dmath*}\breakingcomma
\text{ $\bullet $ V. Shtabovenko, {``}FeynHelpers: Connecting FeynCalc to FIRE and Package-X{''}, Comput. Phys. Commun., 218, 48-65, 2017, arXiv:1611.06793}
\end{dmath*}

\begin{dmath*}\breakingcomma
\text{Furthermore, remember to cite the authors of the tools that you are calling from FeynHelpers, which are}
\end{dmath*}

\begin{dmath*}\breakingcomma
\text{ $\bullet $ }\underline{\text{FIRE}}\;\text{ by A. Smirnov, if you are using functions that begin with FIRE.}
\end{dmath*}

\begin{dmath*}\breakingcomma
\text{ $\bullet $ }\underline{\text{Kira}}\;\text{ by the Kira collaboration, if you are using functions that begin with Kira.}
\end{dmath*}

\begin{dmath*}\breakingcomma
\text{ $\bullet $ }\underline{\text{Package}-X}\;\text{ by H. Patel, if you are using functions that begin with PaX.}
\end{dmath*}

\begin{dmath*}\breakingcomma
\text{ $\bullet $ }\underline{\text{Fermat}}\;\text{ by R. Lewis, if you are using functions that beging with Fer.}
\end{dmath*}

\begin{dmath*}\breakingcomma
\text{ $\bullet $ }\underline{\text{QGRAF}}\;\text{ by P. Nogueira, if you are using functions that begin with QG.}
\end{dmath*}

\begin{dmath*}\breakingcomma
\text{ $\bullet $ }\underline{\text{LoopTools}}\;\text{ by T. Hahn, if you are using functions that begin with LT.}
\end{dmath*}

\begin{dmath*}\breakingcomma
\text{ $\bullet $ }\underline{\text{pySecDec}}\;\text{ by the SecDec collaboration, if you are using functions that begin with PSD.}
\end{dmath*}
\end{document}
